Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-26 Report/ieee_journal.tex
updated_lineno
included antti comments

\newtoggle{includereview}
\newtoggle{enable_dist_fig}
\newtoggle{single_column}
\togglefalse{single_column}
\togglefalse{enable_dist_fig}
\toggletrue{includereview}

@@

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work has been published in ICASSP 2014 conference.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}

@@

\iftoggle{includereview}{
\newpage
\onecolumn
\doublespacing
\section{Response to reviewer comments}
\input{review_comments}
\twocolumn
\newpage
\singlespacing
}

@@

\acused{MU-MIMO}

>>>>

\newtoggle{includereview}
\newtoggle{enable_dist_fig}
\newtoggle{single_column}
\togglefalse{single_column}
\togglefalse{enable_dist_fig}
\togglefalse{includereview}

@@

\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
\author{
	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland. Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}

@@

\iftoggle{includereview}{
\newpage
\onecolumn
\doublespacing
\section{Response to reviewer comments}
\input{review_comments}
\twocolumn
\newpage
\singlespacing
\setcounter{page}{1}
}

@@

### 2015-02-26 Report/introduction.tex
included antti comments

\subsubsection*{Main Contributions}
\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}. The proposed design provides better control over the resource allocation strategy by the change of a variable. Since the transmissions are guided by the backlogged packets, the proposed formulation limits the resource allocation beyond the number of backlogged packets without additional rate constraint. Since the problem is nonconvex due to \ac{DC} constraints, we adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint. First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution. \review{It is worth noting that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.

>>>>

\subsubsection*{Main Contributions}
\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS} queues. Since the transmissions are guided by the backlogged packets, the proposed formulation limit the allocations beyond the number of backlogged packets without additional rate constraint. We adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint. First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders. Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods. Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution. \review{It is worth noting that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.

### 2015-02-26 Report/kkt_mse_approach.tex
included antti comments

\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of the transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed with it. Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem. Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution. Note that it requires four iterations to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders. In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations. If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.}

>>>>

\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of the transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed with it. Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem. Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution. Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders. In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations. If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.}

### 2015-02-26 Report/problem_formulation.tex
included antti comments

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value. \review{In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2,
\end{equation}
which is similar to the objective in \eqref{q_gen_sum}. Note that the equivalence can be seen either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}

>>>>

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value. \review{In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2,
\end{equation}
which is similar to the objective in \eqref{q_gen_sum}. It is achieved either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}

### 2015-02-26 Report/problem_formulation_intro.tex
included antti comments

To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation given by
\begin{equation}
v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}),
\label{eqn-4.2}
\end{equation}
where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}}.

@@

For practical reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total number of backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} for user \me{k} remaining in the system is given by
\begin{equation} \label{rate_constraint_a}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
\end{equation}
The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

>>>>

To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation objective as given by
\begin{equation}
v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}),
\label{eqn-4.2}
\end{equation}
where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receivers \me{\mvec{w}{l,k,n}}.

@@

For practical reasons, we impose a constraint on the maximum number of transmitted bits for the user \me{k}, since it is limited by the total number of backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} for user \me{k} remaining in the system is given by
\begin{equation} \label{rate_constraint_a}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
\end{equation}
The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

### 2015-02-26 Report/simulation_distributed.tex
final version
included antti comments

The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.

Fig. \ref{fig-d} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using the \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} point. In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables. In Fig. \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence. It can be seen from Fig. \ref{fig-d} that the distributed algorithms approach the centralized performance by exchanging minimal information between the coordinating \acp{BS}.

\iftoggle{enable_dist_fig}
{	
In Fig. \ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively. The users are assumed to have the path loss following the uniform distribution between \me{[0,-6]} dB from all \acp{BS}. The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.

Fig. \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update. In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations. In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution. The data tips are used to highlight the convergent points of various algorithms. The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes. It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
\begin{figure*}
	\centering
	\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
		\includegraphics[width=0.48\textwidth]{fig-3-2}
		\label{fig-d-1}
	}
	\hfill
	\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
		\includegraphics[width=0.48\textwidth]{fig-5-1}
		\label{fig-d-2}
	}
	\caption{Number of backlogged packets at each \ac{SCA} points}
	\label{fig-d}
\end{figure*}
% \begin{figure*}
% \centering
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-5}
% \caption{Queue deviation}
% \end{subfigure}
% \hfill
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-6}
% \caption{Sum rate performance}
% \end{subfigure}
% \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
% \label{fig-d-2}
% \end{figure*}
}{
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{fig-3-2}
\caption{Convergence behaviour of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm}}
\label{fig-d}
\end{figure}
}
Fig. \ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents by plotting the total number of backlogged packets at each \ac{SCA} update point. The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one. A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}. It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function. It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-9-3}
	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
	\label{fig-d-3.1}
\end{figure}

@@

>>>>

The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-3-2}
	\caption{Convergence of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
	\label{fig-d}
\end{figure}

Fig. \ref{fig-d} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using the \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} point. In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables. In Fig. \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence. It can be seen from Fig. \ref{fig-d} that the distributed algorithms approach the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-9-3}
	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
	\label{fig-d-3.1}
\end{figure}

Fig. \ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents by plotting the total number of backlogged packets at each \ac{SCA} update point. The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one. A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}. It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function. It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure*}
	\centering
	\subfloat[][Average backlogged packets in the system after \me{100} transmission instants]{
		\includegraphics[width=0.48\textwidth]{average_queue_over_time}
		\label{fig-review}
	}
	\hfill
	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 5} bits]{
		\includegraphics[width=0.48\textwidth]{instant_queue_over_time}
		\label{fig-review-time}
	}
	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
	\label{fig-time-analysis}
\end{figure*}

@@

\begin{comment}

In Fig. \ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively. The users are assumed to have the path loss following the uniform distribution between \me{[0,-6]} dB from all \acp{BS}. The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.

Fig. \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update. In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations. In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution. The data tips are used to highlight the convergent points of various algorithms. The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes. It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
\begin{figure*}[t]
	\centering
	\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
		\includegraphics[width=0.48\textwidth]{fig-3-2}
		\label{fig-d-1}
	}
	\hfill
	\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
		\includegraphics[width=0.48\textwidth]{fig-5-1}
		\label{fig-d-2}
	}
	\caption{Number of backlogged packets at each \ac{SCA} points}
	\label{fig-d}
\end{figure*}

\end{comment}

### 2015-02-26 Report/simulation_intro.tex
included antti comments

The simulations carried out in this work consider the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples. The queues are generated based on the Poisson process with the average values specified in each section presented. 
\begin{table*}
	\centering
	\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm in objective}}
	\label{fig-a}
\end{figure*}

>>>>

The simulations carried out in this work consider the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples. The queues are generated based on the Poisson process with the average values specified in each section presented. 
\begin{table*}
	\centering
	\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}}
	\label{fig-a}
\end{figure*}
